\Title

### 2021-01-08 manuscript/manuscript.tex

>>>>

We have also computed the fitting time ratio for each overlap, in a similar way
we did for the window sizes (see Fig.~\ref{fig:gradient-boosted-overlap}b).

\begin{figure}
    \includegraphics[width=\linewidth]{figs/gradient-boosted-overlap.pdf}
    \caption{
        Gradient-boosted equivalent sources performance against amount of
        overlap.
        (a) Root-mean-squared error between predictions and target grid using
        non-boosted sources (orange dashed line) and gradient-boosted
        equivalent sources (blue dots) for different amount of overlap. Each
        RMS error is the mean of the RMS produced by the same set of parameters
        but with different random seeds.
        (b) Ratio between the computational times needed to fit the
        gradient-boosted and the non-boosted equivalent sources, respectively
        (the fitting time ratio for the non-boosted equivalent sources is
        therefore equal to one).
    }
    \label{fig:gradient-boosted-overlap}
\end{figure}

From the results obtained we can conclude that a lower values of overlap
generates less accurate results, while a higher overlap increases the
computational time required for fitting the source coefficients due to the
significant increment of the number of overlapping windows.

We found that overlaps less than 40\% produce very inaccurate predictions in
comparison with the non-boosted equivalent sources, while values larger that
80\% produce predictions with almost the same level of accuracy as the latter.
Nevertheless, overlap values larger that 70\% takes significantly more
computational time to fit the source coefficients.

THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?

We can then conclude that using overlap values between 40\% and 70\% generate
a balance between predictions accuracy and computational time needed to fit the
source coefficients.
This corroborates that our naive choice of 50\% is good enough for producing
accurate predictions in reasonable times.
